---
output:
  md_document:
    variant: gfm
    pandoc_args: "--wrap=preserve"
# devtools::build_readme()
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinycoreci

<!-- badges: start -->
[![R CMD check](https://github.com/rstudio/shinycoreci/workflows/R-CMD-check/badge.svg)](https://github.com/rstudio/shinycoreci/actions?query=workflow%3AR-CMD-check)
[![Lifecycle Experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This is an R package to install all dependencies to test the bleeding edge of all relevant packages to the Shiny team.

For more direct usage examples, see [`rstudio/shinycoreci-apps`](https://github.com/rstudio/shinycoreci-apps).


## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
remotes::install_github("rstudio/shinycoreci")
```

TODO-barret document about the order
TODO-barret make a testthat test to make sure the remotes are installed in the correct order. Use `shinycoreci:::cached_shinycoreci_remote_deps()` for help

These `Remotes` will be installed to make sure the latest package development is working as expected:

```{r, echo = FALSE, results = "asis"}
pkgs <-
  sort(
    strsplit(
      unname(read.dcf("DESCRIPTION")[1, "Remotes"]),
      "\\n\\s*"
    )[[1]]
  )

# remove branches, sha, and commas
github_pkgs <- sub("[, (@#].*$", "", pkgs)
pkgs <- sub(",", "", pkgs)

# print as links to repos
cat(
  paste0(
    "* [", pkgs, "](http://github.com/", github_pkgs, ")",
    collapse = "\n"
  )
)
```
