---
title: "Shiny Location Kitchen Sink"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    resize_reload: false
runtime: shiny
---

```{r}
library(flexdashboard)
library(shiny)
```

# Inputs: `r renderText({getmonth()})` {.sidebar}

```{r}
selectInput(
  "month",
  label = "Pick a Month",
  choices = month.abb,
  selected = month.abb[2]
)
getmonth <- reactive({
  input$month
})
```

<div id="sidebarContent">

Sidebar Content: `r renderText(getmonth())`

</div>

```{r}
shinyjster::shinyjster_server(input, output, session)
shinyjster::shinyjster_js("
  var jst = jster(1);
  function assert_equal(id, txt) {
    assert_equal_qs('#section-' + id, txt);
  }
  function assert_equal_qs(qs, txt) {
    jst.add(function() {
      var el = $(qs);
      Jster.assert.isEqual(
        el.text().replace(/\s+/g, ''),
        txt,
        {query_string: qs, element: el}
      );
    })
  }

  function assert_page(idx, month) {
    jst.add(Jster.shiny.waitUntilStable);

    jst.add(function() {
      // make sure on first page
      $('a[href=\"#section-p1\"]').click();
    });
    jst.add(function() {
      // make sure first tab is displayed
      $('a[href=\"#section-tab1\"]').click();
    });
    jst.add(Jster.shiny.waitUntilStable);

    jst.add(function() {
      Jster.selectize.click('month');
    });
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(function() {
      Jster.selectize.clickOption('month', idx);
    });

    // Can not use wait until idle for 1000 with flexdashboard
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(Jster.shiny.waitUntilStable);
    jst.add(Jster.shiny.waitUntilStable);

    assert_equal_qs('a[href=\"#section-p1\"]', 'Page 1:\n' + month);
    assert_equal_qs('a[href=\"#section-p2\"]', 'Page 2:\n' + month);
    assert_equal('sidebarContent', 'Sidebar Content: ' + month);

    assert_equal_qs('#section-hidden1 .value-output', 'VB1: ' + month);
    assert_equal_qs('#section-hidden2 .value-output', 'VB2: ' + month);
    assert_equal_qs('#section-hidden3 .value-output', 'VB3: ' + month);

    assert_equal_qs('#section-row2_plotly .chart-title', 'Row 2 Plotly Title: ' + month);
    assert_equal_qs('#section-row2_plotly p', 'Row 2 Plotly Content: ' + month);
    assert_equal_qs('#section-row2_plotly .chart-notes', 'Plotly Caption: ' + month);
    assert_equal_qs('#section-row2_plotly svg .gtitle', month);

    assert_equal_qs('#section-row2_shiny .chart-title', 'Row 2 Shiny Title: ' + month);
    assert_equal_qs('#section-row2_shiny p', 'Row 2 Shiny Content: ' + month);
    assert_equal_qs('#section-row2_shiny .chart-notes', 'Shiny Caption: ' + month);
    jst.add(function() {
      Jster.assert.isEqual(
        $('#section-row2_shiny img').attr('alt'),
        'Shiny plot alt text: ' + month,
        {query_string: \"$('#section-row2_shiny img').attr('alt')\", element: $('#section-row2_shiny img')}
      );
    })

    assert_equal_qs('a[href=\"#section-tab1\"]', 'Tab 1 Title: ' + month);
    assert_equal_qs('#section-tab1 p', 'Tab 1 Content: ' + month);

    jst.add(function() {
      $('a[href=\"#section-tab2\"]').click();
    });
    jst.add(Jster.shiny.waitUntilStable);

    assert_equal_qs('a[href=\"#section-tab2\"]', 'Tab 2 Title: ' + month);
    assert_equal_qs('#section-tab2 p', 'Tab 2 Content: ' + month);

    // test second page
    jst.add(function() {
      $('a[href=\"#section-p2\"]').click();
    });
    jst.add(function() {
      $('a[href=\"#section-p2t1\"]').click();
    });
    jst.add(Jster.shiny.waitUntilStable);

    assert_equal_qs('#section-p2r1 .chart-title', 'P2R1 Title: ' + month);
    assert_equal_qs('#section-p2r1 p', 'P2R1 Content: ' + month);

    assert_equal_qs('#section-p2r1_plot .chart-title', 'P2R1 plot Title: ' + month);
    assert_equal_qs('#section-p2r1_plot p', 'P2R1 plot Content: ' + month);
    assert_equal_qs('#section-p2r1_plot .chart-notes', 'Plot Caption: ' + month);

    assert_equal_qs('a[href=\"#section-p2t1\"]', 'P2T1 Title: ' + month);
    assert_equal_qs('#section-p2t1 p', 'P2T1 Content: ' + month);

    jst.add(function() {
      $('a[href=\"#section-p2t2\"]').click();
    });
    jst.add(Jster.shiny.waitUntilStable);
    assert_equal_qs('a[href=\"#section-p2t2\"]', 'P2T2 Title: ' + month);
    assert_equal_qs('#section-p2t2 p', 'P2T2 Content: ' + month);
  }

  assert_page(1, 'Feb');
  assert_page(5, 'Jun');

  jst.test();
")
```


# Page 1: `r renderText({getmonth()})` {id=p1}


Row
-------------------------------------

### Hidden title 1 {id=hidden1}

```{r}
renderValueBox({
  valueBox({paste0("VB1: ", getmonth())}, "Value Box 1")
})
```

### Hidden title 2 {id=hidden2}

```{r}
renderValueBox({
  valueBox({paste0("VB2: ", getmonth())}, "Value Box 2")
})
```

### Hidden title 3 {id=hidden3}

```{r}
renderValueBox({
  valueBox({paste0("VB3: ", getmonth())}, "Value Box 3")
})
```

Row
-------------------------------------

### Row 2 Plotly Title:  `r renderText(getmonth())` {id=row2_plotly}

Row 2 Plotly Content: `r renderText(getmonth())`

```{r}
library(plotly)
renderPlotly({
  cars %>%
    plot_ly(x = ~ speed, y = ~ dist) %>%
    add_markers() %>%
    layout(title = getmonth())
})
```

> Plotly Caption: `r renderText(getmonth())`

### Row 2 Shiny Title:  `r renderText(getmonth())` {id=row2_shiny}

Row 2 Shiny Content: `r renderText(getmonth())`

```{r}
renderPlot({
  plot(cars, main = getmonth())
}, alt = reactive({ paste0("Shiny plot alt text: ", getmonth()) }) )

```

> Shiny Caption: `r renderText(getmonth())`



Row {.tabset}
-------------------------------------

### Tab 1 Title:  `r renderText(getmonth())` {id=tab1}

Tab 1 Content: `r renderText(getmonth())`

```{r}
knitr::kable(mtcars)
```

### Tab 2 Title:  `r renderText(getmonth())` {id=tab2}

Tab 2 Content: `r renderText(getmonth())`

```{r}
renderTable({
  head(mtcars, n = 12)
})
```


# Page 2: `r renderText({getmonth()})` {id=p2}


Row
-------------------------------------

### P2R1 Title:  `r renderText(getmonth())` {id=p2r1}

P2R1 Content: `r textOutput("p2r1content", inline = TRUE)`

```{r}
output$p2r1content <- renderText(getmonth())
```

### P2R1 plot Title:  `r renderText(getmonth())` {id=p2r1_plot}

P2R1 plot Content: `r renderText(getmonth())`

```{r, fig.width=10, fig.height=7}
plot(ldeaths, main = "Static title")
```

> Plot Caption: `r renderText(getmonth())`


Row {.tabset}
-------------------------------------

### P2T1 Title:  `r renderText(getmonth())` {id=p2t1}

P2T1 Content: `r renderText(getmonth())`

### P2T2 Title:  `r renderText(getmonth())` {id=p2t2}

P2T2 Content: `r renderText(getmonth())`
